Evolution of a conspicuous dynamic visual signal in an introduced chameleon

### 2021-05-08 ms.Rmd
Fixed spelling mistakes, added some spaces for subscripts

table1 <- as.data.frame(rbind(robust_ConspicDisplayAC_CI,
                robust_ConspicDisplayCC_CI,
                robust_ConspicCourtshipAC_CI,
                robust_ConspicCourtshipCC_CI))
table1$Parameter <- rownames(table1)
rownames(table1) <- NULL
# Clean
 final_T1 <- table1 %>% 
             mutate(SocialContext = c("Male-Male Display", rep("", 5), "Courtship Display", rep("", 5)),
                    VisualRealm = c("Acromatic Contrast", rep("", 2), "Chromatic Contrast", rep("", 2), "Acromatic Contrast", rep("", 2), "Chromatic Contrast", rep("", 2))) %>%
              select(SocialContext, VisualRealm, Parameter, beta, SE, df, CI_L, CI_U)

@@

# Clean
 final_T2 <- table2 %>% 
             mutate(JND = c("Acromatic Contrast", rep("", 3), "Chromatic Contrast", rep("", 3))) %>%
              select(JND, Parameter, beta, SE, df, CI_L, CI_U)

@@

tb4 <- tb4 %>% mutate(SocialContext = c("Male-Male Display", rep("", 5), 
                                        "Courtship Display", rep("", 5)),
                    VisualRealm = c("Acromatic Contrast", rep("", 2), "Chromatic Contrast", 
                                    rep("", 2), "Acromatic Contrast", rep("", 2), 
                                    "Chromatic Contrast", rep("", 2))) %>%
              select(SocialContext, VisualRealm, parameter, beta, SE, df, CI_L, CI_U)

>>>>

table1 <- as.data.frame(rbind(robust_ConspicDisplayAC_CI,
                robust_ConspicDisplayCC_CI,
                robust_ConspicCourtshipAC_CI,
                robust_ConspicCourtshipCC_CI))
table1$Parameter <- rownames(table1)
rownames(table1) <- NULL
# Clean
 final_T1 <- table1 %>% 
             mutate(SocialContext = c("Male-Male Display", rep("", 5), "Courtship Display", rep("", 5)),
                    VisualRealm = c("Achromatic Contrast", rep("", 2), "Chromatic Contrast", rep("", 2), "Achromatic Contrast", rep("", 2), "Chromatic Contrast", rep("", 2))) %>%
              select(SocialContext, VisualRealm, Parameter, beta, SE, df, CI_L, CI_U)

@@

# Clean
 final_T2 <- table2 %>% 
             mutate(JND = c("Achromatic Contrast", rep("", 3), "Chromatic Contrast", rep("", 3))) %>%
              select(JND, Parameter, beta, SE, df, CI_L, CI_U)

@@

tb4 <- tb4 %>% mutate(SocialContext = c("Male-Male Display", rep("", 5), 
                                        "Courtship Display", rep("", 5)),
                    VisualRealm = c("Achromatic Contrast", rep("", 2), "Chromatic Contrast", 
                                    rep("", 2), "Achromatic Contrast", rep("", 2), 
                                    "Chromatic Contrast", rep("", 2))) %>%
              select(SocialContext, VisualRealm, parameter, beta, SE, df, CI_L, CI_U)
